\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Wayne Havey Journal \#5\\
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Wayne R. Havey III}
\IEEEauthorblockA{\textit{PhD Student: Security Track} \\
\textit{UCCS}\\
Colorado Springs, CO \\
whavey@uccs.edu}
}

\maketitle

\section{Survey Paper Learning}
This last week I started refining the survey paper by filling in the gaps I left in the draft. The first draft I spent more time making more of a list that represented the classification approach and didnt really fill in a lot of the meat of the paper with the exception of the abstract and a bit of the introduction. I learned that I feel like Im bad at introductions. I had a hard time distinguishing what should go into it. I tried making it somewhat story based by calling out the reader as a cyber detective. I think it could work after some more refinement. Filling in the meat of the other sections has been easier than I expected. \\
Ive been learning that the classification is constantly in flux as far as what I want to actually be a part of it and what should be high level categories as opposed to subcategories. Based on the feedback I received I learned its easy to have the classification turn into more of a list. Theres a fine line between categorization thats too high level and just a list and figuring out that sweet spot may take some time. I think actually drawing out the figure better may help shed some light on that. \\
I also learned that there are many surveys that present classifications of some of my subcategories but not really anything that presents my exact approach and in the way Im presenting it. Most surveys seem interested in parts of detection techniques but don't really address the actual literature as much as I think I am. 
\end{document}
